The Dynamics of Normalization Reweighting (target journal: Neuron)

### 2022-05-22 manuscript.Rmd
Updates to analysis code

---
title: "The Dynamics of Normalization Reweighting"
author: "Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning, Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade"
date: "`r Sys.Date()`"
output: html_document
---

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}

@@

@@

samplerate <- 1001
targetF <- 5
maskF <- 7
    binwidth <- 1001
    tindex <- 1 + targetF*(binwidth/1001)
    mindex <- 1 + maskF*(binwidth/1001)

d <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=TRUE)
d2 <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=FALSE)

@@

# par(mfrow=c(2,3))

>>>>

---
title: "The Dynamics of Normalization Reweighting (target journal: Neuron)"
author: "Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning, Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade"
date: "`r Sys.Date()`"
output: html_document
---

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}

@@

samplerate <- 1000
targetF <- 5
maskF <- 7
    binwidth <- 1000
    tindex <- 1 + targetF*(binwidth/samplerate)
    mindex <- 1 + maskF*(binwidth/samplerate)

d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)

groupmeans <- array(0,dim=c(length(d),4,4,10))
groupspec <- array(0,dim=c(length(d),4,64,121))
groupspecplot <- array(0,dim=c(length(d),4,121))
groupwaveforms <- array(0,dim=c(length(d),4,8000))
EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))

for (s in 1:length(d)){
  load(d[s])

  # remove any NaN values
  chanspec[which(is.na(chanspec))] <- 0
  allspec[which(is.na(allspec))] <- 0
  allsamples[which(is.na(allsamples))] <- 0

  ch <- match(toupper(targetelectrodes),toupper(electrodes),nomatch=0)

  meanchanspec <- (apply(chanspec,2:4,mean))
  spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))

  meanspec <- (apply(allspec,2:4,mean))
  for (f in 1:4){
    for (cond in 1:4){
      for (t in 1:10){
        temp <- allspec[,f,cond,t]
        tempxy <- data.frame(Re(temp),Im(temp))
        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
        i <- which(D<3)
        meanspec[f,cond,t] <- (mean(temp[i]))
      }
    }
  }
  meanwaves <- apply(allsamples,2:3,mean)

  for (cond in 1:4){
   fspec1 <- NULL
fspec2 <- NULL
for (t in 1:(8000-binwidth)){
  spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
  fspec1[t] <- spec[tindex]
  fspec2[t] <- spec[mindex]
}
    EEGtimecourse5Hz[s,cond,] <- fspec1
    EEGtimecourse7Hz[s,cond,] <- fspec2 
  }

  meanwaves <- meanwaves - mean(meanwaves)
  meanwaves <- meanwaves / max(abs(meanwaves))
  groupmeans[s,,,] <- meanspec
  groupspec[s,,,] <- meanchanspec
  groupspecplot[s,,] <- spectoplot
  groupwaveforms[s,,] <- meanwaves

meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
meanwaves <- apply(groupwaveforms,c(2,3),mean)
meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))

EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
for (cond in 1:4){
EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
}

par(mfrow=c(2,2))

times <- ((1:7000)-500)/1000

plotlims <- c(-1,8,0,1)
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
ticklabelsx <- -1:8        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')

spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
lines(spl5a$x,spl5a$y,col='red',lwd=2)
spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
lines(spl5b$x,spl5b$y,col='green',lwd=2)
spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
lines(spl5c$x,spl5c$y,col='blue',lwd=2)
spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
lines(spl5d$x,spl5d$y,col='orange',lwd=2)

plotlims <- c(-1,8,0,2) 
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
ticklabelsx <- -1:8        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)

lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)

plotlims <- c(-1,8,0,1) 
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')

spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
lines(spl7a$x,spl7a$y,col='red',lwd=2)
spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
lines(spl7b$x,spl7b$y,col='green',lwd=2)
spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
lines(spl7c$x,spl7c$y,col='blue',lwd=2)
spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
lines(spl7d$x,spl7d$y,col='orange',lwd=2)

plotlims <- c(-1,8,0,2) 
ticklocsx <- -1:8    # locations of tick marks on x axis
ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
ticklabelsx <- -1:8        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)

@@

samplerate <- 1001
targetF <- 5
maskF <- 7
    binwidth <- 1001
    tindex <- 1 + targetF*(binwidth/samplerate)
    mindex <- 1 + maskF*(binwidth/samplerate)

# d <- dir(path = 'temp/V2/', pattern = '*alltrialsV2.mat', full.names=TRUE)
# d2 <- dir(path = 'temp/V2/', pattern = '*alltrialsV2.mat', full.names=FALSE)
d <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=TRUE)
d2 <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=FALSE)

@@

par(mfrow=c(2,2))
